---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

## Overview
The `cyclingdata` package presents a comprehensive dataset on major stage races in professional cycling. 
The data includes 11,125 stages over the past 120 years from all three Grand Tours (Tour de France, Giro d'Italia, La Vuelta Ciclista a España) in addition to Critérium du Dauphiné, Itzulia Basque Country, Paris-Nice, Tirreno-Adriatico, Tour de Pologne, Tour de Romandie, Tour de Suisse, and Volta Ciclista a Catalunya. (Source: https://www.procyclingstats.com)

The package also contains [cyclingscraper()] which enable users to scrape cycling data directly from https://www.procyclingstats.com. 

## Installation

``` r
# Install the development version from GitHub
devtools::install_github("jenslemb/cyclingdata")
```

## Usage

### Access cyclingdata

You can access the data simply by loading the package and calling `cyclingdata`. 
You can find more info about the data in the *reference section*

```{r, eval=FALSE}
library(cyclingdata)

cyclingdata
```

#### Select races or years 

You can subset data using regular methods. Below is an example using `dplyr`. 

```{r, eval=FALSE}
library(dplyr)

cyclingdata |> 
  filter(race == "Tour de France")

cyclingdata |> 
  filter(year == 2023)
```

### Scraping data

`cyclingscraper()` allows you to scrape race data directly from https://www.procyclingstats.com.
You can request multiple races and years. Please see the reference section for more details about
accepted arguments. 

```{r, eval=FALSE}
cyclingscraper(races = c("tdf", "giro", "vuelta"), years = 2022:2023)
```


## Getting help
If you encounter a clear bug, please file an issue with a minimal reproducible example on GitHub. You are also more than welcome to shoot me an email at [githubusername]@gmail.com if you have questions or comments.


## Future releases
I am currently working on adding more races, including monuments and other major one-day races. I will also add race results and rider info in the future. Follow updates in the News section.



